---
title: "Vectorized Computing"
author: "Jun Mei"
date: "November 27, 2017"
output: 
  ioslides_presentation: 
    transition: faster
---

## Matrix multiplication | A = BxC

```{python eval=FALSE}
for i in range(m):
  for j in range(n):
    for k in range(r):
      A[i][j] += B[i][k] * C[k][j]
```

## Matrix multiplication | Vectorized

```{python eval=FALSE}
for i in range(m):
  for j in range(n):
    A[i, j] = np.sum(B[i, :] * C[:, j])
```

```{python eval=FALSE}
for i in range(m):
  for j in range(n):
    for k in range(r):
      A[i][j] += B[i][k] * C[k][j]
```

## Matrix multiplication | Fully vectorized

```{python eval=FALSE}
m_r_n = B.reshape(m, r, 1) * C.reshape(1, r, n)
A = np.sum(m_r_n, axis=1)
```

```{python eval=FALSE}
for i in range(m):
  for j in range(n):
    for k in range(r):
      A[i][j] += B[i][k] * C[k][j]
```

## Boardcasting

```{python}
import numpy as np
B = np.array([[0, 1]])  # shape: 1x2
C = np.array([[0],
              [1],
              [2]])  # shape: 3x1
A = B + C
print(A)
```

## Floyd-Warshall algorithm

G is an nxn adjacency matrix

```{python eval=FALSE}
for k in range(n):
  for i in range(n):
    for j in range(n):
      G[i][j] = min(G[i][j], G[i][k] + G[k][j])
```

## Floyd-Warshall algorithm | Vectorized

```{python eval=FALSE}
for k in range(n):
  n_n = G[:, k].reshape(n, 1) + G[k, :].reshape(1, n)
  G = np.minimum(G, n_n)
```

```{python eval=FALSE}
for k in range(n):
  for i in range(n):
    for j in range(n):
      G[i][j] = min(G[i][j], G[i][k] + G[k][j])
```

## Experiments

- Warm-up-time limit: 1 minute
- Cratical-time limit: 1 second

```{r echo=FALSE}
library(ggplot2)
library(scales)
f0 <- read.csv("src/floyd/summary.csv")
m0 <- read.csv("src/matmul/summary.csv")
lp <- function(df) {
	ggplot(df, aes(x=N, y=Time, col=Method)) +
		geom_line() +
		geom_point() +
		scale_x_continuous(trans=log2_trans()) +
		scale_y_log10()
}
```

## Floyd-Warshall algorithm

```{r echo=FALSE}
lp(f0)
```

----

for_python << for_go < for_java < for_c

```{r echo=FALSE}
f1 <- f0[f0$Method %in% c("for_c", "for_go", "for_java", "for_python"),]
lp(f1)
```


----

k_tf < k_torch < k_numpy < for_java < for_c (N <= 4)

```{r echo=FALSE}
f1 <- f0[f0$Method %in% c("for_c", "for_java", "k_numpy", "k_torch", "k_tf"),]
lp(f1)
```

----

k_numpy = k_tf = k_torch = for_java < for_c

```{r echo=FALSE}
f1 <- f0[f0$Method %in% c("for_c", "for_java", "k_numpy", "k_torch", "k_tf"),]
f2 <- f1[f1$N >= 128,]
lp(f2)
```

----

for_java < for_c < k_tf_gpu = k_torch_gpu

```{r echo=FALSE}
f1 <- f0[f0$Method %in% c("for_c", "for_java", "k_torch_gpu", "k_tf_gpu"),]
lp(f1)
```

## Matrix multiplication

```{r echo=FALSE, fig.height=5.5}
lp(m0)
```

----

for_python << for_go < for_java <= for_c

```{r echo=FALSE}
m1 <- m0[m0$Method %in% c("for_c", "for_go", "for_java", "for_python"),]
lp(m1)
```

----

ij_*_gpu < ij_tf < ij_numpy = ij_torch < for_+

```{r echo=FALSE}
m1 <- m0[m0$Method %in% c("for_c", "for_java", "ij_numpy", "ij_tf", "ij_torch", "ij_tf_gpu", "ij_torch_gpu"),]
lp(m1)
```

----

full_cpu < for_+ < full_tf_gpu < full_torch_gpu

```{r echo=FALSE, fig.height=5.5}
m1 <- m0[m0$Method %in% c("for_c", "for_java", "full_numpy", "full_tf", "full_torch", "full_tf_gpu", "full_torch_gpu"),]
lp(m1)
```

----

for_+ < full_\*gpu < mat_\*

```{r echo=FALSE, fig.height=5.5}
m1 <- m0[m0$Method %in% c("for_c", "for_java", "full_tf_gpu", "full_torch_gpu", "mat_numpy", "mat_tf", "mat_torch", "mat_tf_gpu", "mat_torch_gpu"),]
lp(m1)
```

----

tf_gpu < tf < torch_gpu < torch < numpy (N < 128)

```{r echo=FALSE, fig.height=5.5}
m1 <- m0[m0$Method %in% c("mat_numpy", "mat_tf", "mat_torch", "mat_tf_gpu", "mat_torch_gpu"),]
lp(m1)
```

----

tf < numpy < torch < tf_gpu < torch_gpu

```{r echo=FALSE, fig.height=5.5}
m1 <- m0[m0$Method %in% c("mat_numpy", "mat_tf", "mat_torch", "mat_tf_gpu", "mat_torch_gpu"),]
m2 <- m1[m1$N >= 128,]
lp(m2)
```

## Conclusion

> - The code is avaiable
  - at https://github.com/meijun/vectorized-computing
